\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Aldemar Villegas}}\\
	Cali, Valle del Cauca, Colombia $\cdot$ alvilleg@gmail.com $\cdot$ (57) 3127584992 $\cdot$ upwork.com\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{Universidad del Valle}\hfill Cali, Valle del Cauca\\
BS Ingeniero de Sistemas \textit{GPA: 4.2} \hfill Aug 2001 - Oct 2006\\
\vspace{2mm}





\header{Projects}
{\textbf{Perseus}} {\sl Java, Javascript, Spring Framework, AngularJS} \\
Vehicle Routing Solver\\
\vspace*{2mm}
{\textbf{Geodec}} {\sl Java, Postgresql, MongoDB, Openlayers, MariaDB Columnar Store} \\
Address geocoder, map viewer, OLAP Viewer\\
\vspace*{2mm}

\header{Awards}
\textbf{Andres Bello} \hfill ICFES\\
Recognized for hight score in standard tests, scholarship to study in the University \hfill Nov 1999\\
\vspace*{2mm}

\ 
\end{document}%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Gayle L. McDowell}
\address{123 Spruce St, Apt 35 \linebreak Philadelphia PA 19103}
\contacts{(555) 555-1212 \linebreak gayle@careercup.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Software Engineer, Intern}{Apple Computer}{Summer 2004}
			iChat AV			
			\begin{itemize}
				\item Reduced time to render the user’s buddy list by 75\% by implementing prediction algorithm.
				\item Implemented iChat integration with OS X Spotlight Search by creating tool which extracts metadata from saved chat transcripts and provides metadata to a system-wide search database.
				\item Redesigned chat file format and implemented backwards compatibility for search.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Lead Student Ambassador}{Microsoft Corporation}{Fall 2003 -- Spring 2005}	
			\begin{itemize}
				\item Promoted to Lead Student Ambassador in Fall 2004; supervised 10 -- 15 Student Ambassadors.
				\item Created and taught Computer Science course, CSE 099: Software Design and Development.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Head Teaching Assistant}{University of Pennsylvania}{Fall 2001 -- Spring 2005}		
			\begin{itemize}
				\item Courses: Advanced Java III, Software Engineering, Mathematical Foundations of Computer Science I \& II.
				\item Promoted to Head TA in Fall 2004; led weekly meetings and supervised four other TAs.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Design Engineer, Intern}{Microsoft Corporation}{Summers 2001 -- 2003}
			Visual Studio Core (Summer 2003)		
			\begin{itemize}
				\item Implemented a user interface for the VS open file switcher (ctrl-tab) and extended it to tool windows.
				\item Created service to provide gradient across VS and VS add-ins. Optimized service via caching.
			\end{itemize}
			Programmer Productivity Research Center (Summers 2001, 2002)
			\begin{itemize}
				\item Built app to compute similarity of all methods in a code base; reduced time from $O(n^2)$ to $O(n\ log\ n)$. 
				\item Created test case generation tool which creates random XML docs from XML Schema.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Philadelphia, PA}{University of Pennsylvania}{Fall 2000 -- May 2005}
			\begin{itemize}
				\item M.S.E. in Computer and Information Science, May 2005. GPA: 3.6
				\item B.S.E. in Computer Science Engineering with Minor in Mathematics, May 2005.  In-major GPA: 3.4.
				\item Graduate Coursework: Software Foundations; Computer Architecture; Algorithms; Artificial Intelligence; Comparison of Learning Algorithms; Computational Theory.
				\item Undergraduate Coursework: Operating Systems; Databases; Algorithms; Programming Languages; Comp. Architecture; Engineering Entrepreneurship; Calculus III.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{Multi-User Drawing Tool} (2004). Electronic classroom where multiple users can view and simultaneously draw on a “chalkboard” with each person’s edits synchronized.  C++, MFC
				\item \textbf{Synchronized Calendar} (2003 – 2004). Desktop calendar with globally shared and synchronized calendars, allowing users to schedule meetings with other users.  C\#.NET, SQL, XML
				\item \textbf{Operating System} (2002).  UNIX-style OS with scheduler, file system, text editor and calculator. C
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Additional Experience and Awards}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Instructor (2003 – 2005):} Taught two full-credit Computer Science courses; average ratings of 4.8 out of 5.0.
				\item \textbf{Third Prize, Senior Design Projects:} Awarded 3rd prize for Synchronized Calendar project, out of 100 projects.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item C++; C; Java; Objective-C; C\#.NET; SQL; JavaScript; XSLT; XML (XSD) Schema 
				\item Visual Studio; Microsoft SQL Server; Eclipse; XCode; Interface Builder
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
